Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits

### 2016-03-09 ms.tex
more casey corrections

Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The result is a 398.49 sq. degree mock catalog occupying a $60 \leq RA \leq 90$ and $-40 \leq DEC \leq -61$ portion of the sky. It contains 238 million galaxies with \sdssr\ mag $< 29$ and $z \leq 8.7$.

@@

\subsection{Mass estimates}
\begin{table*}
\centering
\caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions. See the text for discussion about the MAE and RMSE. Overlap is the percentage of clusters where the true cluster mass is bracketed by the prediction intervals of the predicted mass. See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
\begin{tabular}{cccccccc}
	%\hline
	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
	\cline{3-5} \cline{6-8}
	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
	\hline
	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
	\hline
	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
	\hline
\end{tabular}
\label{tbl:mass comparisons}
\end{table*}

In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations. We report on two methods the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}). For each method we consider both targeted and HETDEX-like observing strategies.

We include the cluster masses recovered through the power law scaling relation given in Equation \ref{eq:power law} for the perfect, targeted and survey observations. It should serve as baseline to compare the probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the median absolute error (MAE) 
\begin{equation}
\mathrm{MAE}(y,\hat{y}) = \mathrm{median}(|y_1 - \hat{y_1}|, \ldots, |y_n - \hat{y_n}|) \nonumber
\end{equation}
where $y$ is the true value and $\hat{y}$ is the predicted value, and the root mean squared error (RMSE)
\begin{equation}
	\mathrm{RMSE}(y,\hat{y}) = \bigg{[}\frac{1}{N} \sum_{i=0}^N (y_i - \hat{y_i})^2 \bigg{]}^{1/2}.\nonumber
\end{equation} 
Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases lower numbers are better.

Just because a predicted cluster mass may not exactly match the true value does not mean it is a bad prediction. In addition to the MAE and RMSE, we also report the fraction of predictions where the the true cluster mass is contained within the 68\% confidence or prediction intervals (see Sections \ref{sec:probability method} and \ref{sec:machine learning method}).

The cluster masses predicted by Equation \ref{eq:power law} gives the following results. The MAE is 0.263 dex and for both the targeted and survey observations. The RMSE is 0.396 dex and 0.394 dex for the targeted and survey observations respectively. This scatter in recovered masses can be attributed to both physical and numerical effects. As the cluster mass increases, clusters become more virialized and contain many individual galaxies. The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which can increase the observed LOSVD increasing the predicted mass. Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects. The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method. \editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs. We could do something similar and have a similar discussion, but I'm not sure it is worth it. Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO. We should also talk about how often the true mass lies within the error bars. Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}

@@

@@

The MAE and RMSE associated with the ensemble of predictions are summarized in Table \ref{tbl:mass comparisons}. As expected, we find that both the probability based and ML based methods out perform the standard power law based methods for both the targeted and survey observations. We also find that the ML based method produces lower ensemble error for both the observation strategies when compared to the probability based method, although the MAE and RMSE are reduced by only $\sim0.01$ dex. \editorial{here is where we would talk about cross validation on the errors.}

In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted versus true cluster masses for each of the two observing strategries. In each panel the solid black line is the 1:1 relationship, the solid colored line is the median recovered mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles). The lower panels show the fractional cluster mass error: 
\begin{equation}\label{eq: fractional error}
	\epsilon = (M_{pred} - M)/M
\end{equation}
where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.

In both figures we successively add additional information to further constrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}). The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses. Both the probability and ML methods over predict the mass of low mass clusters and under predict the mass of the higher mass clusters. When the redshift information is also added, the amount of this over and under prediction is lessened but the cross over point, remains roughly consistent at $\sim10^{14}$ \msol. Additionally, the number of galaxies observed, $N_{gal}$, further reduces the MAE and RMSE on the predictions but also lowers the cross over point to $\sim10^{13.5}$ \msol.

% \editorial{It doesn't look like you can use the targeted training sample to train the survey data. If you do, it either does worse or about the same if you didn't use any training at all. After looking at it, you do have to use the survey training data to get good results about 0.13 dex MAE
% }

@@

\begin{table*}
\centering
\caption{Associated mass prediction errors (MAE) for different bins of predicted mass. This table shows the relative error for the targeted (top section) and survey (bottom section) observations for different predicted mass bins. The values in the table correspond to the MAE for the galaxies in the predicted mass bin (top row) for the different mass recovery strategies (leftmost column). It can be used to understand how precise the predicted cluster mass is.}
\begin{tabular}{cccccccccc} 
		&& \multic{8}{Bins -- Log $M_{pred}$ ($\Msol$)} \\
		\cline{3-10} 
		\multicolumn{2}{c}{Input Features} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline 
		\rottext{4}{Prob Based} & Power Law & 0.602 & 0.376 & 0.340 & 0.278 & 0.225 & 0.177 & 0.114 & 0.041 \\
		&$\sigma$ & 1.030 & 0.655 & 0.389 & 0.212 & 0.160 & 0.158 & 0.224 & 0.328 \\
		&$\sigma, z$ & 0.804 & 0.476 & 0.242 & 0.173 & 0.170 & 0.210 & 0.353 & 0.529 \\
		&$\sigma, z, N_{gal}$ & 0.649 & 0.372 & 0.163 & 0.124 & 0.113 & 0.111 & 0.105 & 0.241 \\
		\hline
		\rottext{4}{ML Based} & Power Law & 0.602 & 0.376 & 0.340 & 0.278 & 0.225 & 0.177 & 0.114 & 0.041 \\
		&$\sigma$ & 0.773 & 0.557 & 0.287 & 0.210 & 0.230 & 0.267 & 0.337 & 0.323 \\
		&$\sigma, z$ & 0.631 & 0.380 & 0.211 & 0.172 & 0.182 & 0.236 & 0.284 & 0.265 \\
		&$\sigma, z, N_{gal}$ & 0.539 & 0.304 & 0.148 & 0.117 & 0.105 & 0.095 & 0.078 & 0.110 \\
		\hline 
		\hline
		\rottext{4}{Prob Based} & Power Law & \nd & \nd & 0.520 & 0.319 & 0.263 & 0.214 & 0.140 & 0.069 \\
		&$\sigma$ & \nd & \nd & 0.765 & 0.434 & 0.198 & 0.149 & 0.163 & 0.346 \\
		&$\sigma, z$ & \nd & \nd & 0.592 & 0.305 & 0.162 & 0.165 & 0.257 & 0.396 \\
		&$\sigma, z, N_{gal}$ & \nd & \nd & 0.476 & 0.171 & 0.125 & 0.141 & 0.141 & 15.002 \\
		\hline
		\rottext{4}{ML Based} & Power Law & \nd & 0.583 & 0.316 & 0.337 & 0.278 & 0.214 & 0.140 & 0.069 \\
		&$\sigma$ & \nd & 0.606 & 0.551 & 0.263 & 0.201 & 0.227 & 0.200 & 0.192 \\
		&$\sigma, z$ & \nd & 0.916 & 0.434 & 0.206 & 0.171 & 0.205 & 0.249 & 0.202 \\
		&$\sigma, z, N_{gal}$ & \nd & 0.780 & 0.401 & 0.155 & 0.129 & 0.136 & 0.145 & 0.142 \\
		\hline
	\end{tabular}
\label{tbl:sersic number bins}
\end{table*}

@@

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

It is the author's hope that this work may be useful to others when conducting their own research. Because this work relies heavily on (often) complex data analysis, and in order to promote transparency, we provide all of the code used to conduct this study at https://github.com/boada/desCluster. Regrettably, large file size prevents including the source data with the analysis routines. The authors are happy to provide them, if requested.

>>>>

Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The result is a 398.49 sq. degree mock catalog occupying a $4^h \leq RA \leq 6^h$ and $-61\degree < DEC < -41\degree$ portion of the sky. It contains 238 million galaxies with \sdssr\ mag $< 29$ and $z \leq 8.7$.

@@

\subsection{Mass estimates}
% \begin{table*}
% \centering
% \caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions. See the text for discussion about the MAE and RMSE. Overlap is the percentage of clusters where the true cluster mass is bracketed by the prediction intervals of the predicted mass. See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
% \begin{tabular}{cccccccc}
% 	%\hline
% 	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
% 	\cline{3-5} \cline{6-8}
% 	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
% 	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
% 	\hline
% 	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
% 	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
% 	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
% 	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
% 	\hline
% 	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
% 	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
% 	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
% 	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
% 	\hline
% \end{tabular}
% \label{tbl:mass comparisons}
% \end{table*}

@@

In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations. We report on three methods, the power law based approach (Eq. \ref{eq:power law}), the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}). For each method we consider observations with perfect knowledge, targeted observations and survey observations.

Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias 
\begin{equation}
\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).\nonumber
\end{equation}
where $y$ is the true value and $\hat{y}$ is the predicted value, and the scatter about the bias
\begin{equation}
	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}\nonumber
\end{equation}
for different bins of cluster mass. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.

We begin with the perfect knowledge observations. These observations are of the same clusters as the targeted observations but without any observational limits. The cluster masses predicted by Equation \ref{eq:power law} gives the following results. Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.24}$ dex. The scatter in recovered masses can be attributed to both physical and numerical effects. The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which increases the observed LOSVD increasing the predicted mass \citeeg{Ntampaka2015}. Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects. The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.

\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs. We could do something similar and have a similar discussion, but I'm not sure it is worth it. Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO. We should also talk about how often the true mass lies within the error bars. Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}

For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.37}$ dex and $\mu_{bias} =0.11\pm{0.36}$ dex, respectively. So while, both realistic observations have similar levels of bias, the amount of scatter significantly decreases as more cluster member galaxies are detected, better sampling the LOSVD PDF.

@@

In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted versus true cluster masses for each of the two observing strategries. In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles). For reference we also show the median masses recovered with perfect knowledge as a solid orange line. The lower panels show the fractional cluster mass error: 
\begin{equation}\label{eq: fractional error}
	\epsilon = (M_{pred} - M)/M
\end{equation}
where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.

Qualitatively, the top panels of Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison} show that both the probability based and ML based methods out perform (closer to the black 1:1 relation) the power law method when taking advantage of other cluster observables ($z$, $N_{gal}$, etc.). Generally, we find that the single parameter probability and ML methods perform significantly poorer than the power law method, especially at low cluster masses. When combined with the cluster redshift, the predicted cluster masses are improved, even though it is unclear exactly why the additional information should effect the predicted cluster mass. The final addition of the number of observed galaxies, $N_{gal}$ acts as a type of richness estimate, and significantly improves both the bias and the amount of scatter in the predicted masses.

% In both figures we successively add additional information to further constrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}). The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses. Both the probability and ML methods over predict the mass of low mass clusters and under predict the mass of the higher mass clusters. When the redshift information is also added, the amount of this over and under prediction is lessened but the cross over point, remains roughly consistent at $\sim10^{14}$ \msol. Additionally, the number of galaxies observed, $N_{gal}$, further reduces the MAE and RMSE on the predictions but also lowers the cross over point to $\sim10^{13.5}$ \msol.

% \editorial{It doesn't look like you can use the targeted training sample to train the survey data. If you do, it either does worse or about the same if you didn't use any training at all. After looking at it, you do have to use the survey training data to get good results about 0.13 dex MAE
% }
\begin{table*}
\centering
\caption{Bias and scatter of the true cluster mass for different bins of predicted cluster mass. This table shows the offset and scatter in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccccc} 
		&& \multic{8}{Bins -- Log $M_{pred}$ ($\Msol$)} \\
		\cline{3-10} 
		\multicolumn{2}{c}{Method} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline 
		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
		&$\sigma$ & $0.87\pm{0.15}$ & $0.53\pm{0.24}$ & $0.32\pm{0.26}$ & $0.16\pm{0.20}$ & $0.10\pm{0.16}$ & $0.07\pm{0.14}$ & $0.05\pm{0.16}$ & $-0.18\pm{0.17}$ \\
		&$\sigma, z$ & $0.76\pm{0.16}$ & $0.42\pm{0.21}$ & $0.17\pm{0.23}$ & $0.01\pm{0.19}$ & $-0.06\pm{0.16}$ & $-0.11\pm{0.55}$ & $-0.14\pm{0.16}$ & $-0.38\pm{0.34}$ \\
		&$\sigma, z, N_{gal}$ & $0.65\pm{0.10}$ & $0.28\pm{0.14}$ & $0.04\pm{0.47}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.05\pm{0.54}$ & $-0.22\pm{1.61}$ & $-6.62\pm{8.08}$ \\
		\hline
		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
		&$\sigma$ & $0.69\pm{0.20}$ & $0.36\pm{0.27}$ & $0.15\pm{0.29}$ & $-0.02\pm{0.24}$ & $-0.07\pm{0.21}$ & $-0.09\pm{0.19}$ & $-0.11\pm{0.18}$ & $-0.12\pm{0.19}$ \\
		&$\sigma, z$ & $0.62\pm{0.18}$ & $0.33\pm{0.22}$ & $0.12\pm{0.25}$ & $-0.01\pm{0.20}$ & $-0.06\pm{0.18}$ & $-0.09\pm{0.16}$ & $-0.11\pm{0.17}$ & $-0.19\pm{0.13}$ \\
		&$\sigma, z, N_{gal}$ & $0.51\pm{0.14}$ & $0.23\pm{0.18}$ & $0.05\pm{0.17}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.02\pm{0.08}$ & $-0.02\pm{0.08}$ & $-0.08\pm{0.08}$ \\
		\hline 
		\hline
		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.31}$ & $0.27\pm{0.41}$ & $0.20\pm{0.43}$ & $0.13\pm{0.39}$ & $0.10\pm{0.33}$ & $0.09\pm{0.27}$ & $0.02\pm{0.18}$ & $-0.08\pm{0.09}$ \\
		&$\sigma$ & $1.02\pm{0.13}$ & $0.66\pm{0.19}$ & $0.40\pm{0.24}$ & $0.17\pm{0.25}$ & $0.02\pm{0.25}$ & $-0.08\pm{0.22}$ & $-0.19\pm{0.19}$ & $-0.35\pm{0.26}$ \\
		&$\sigma, z$ & $0.85\pm{0.18}$ & $0.49\pm{0.20}$ & $0.25\pm{0.24}$ & $0.08\pm{0.24}$ & $-0.06\pm{0.23}$ & $-0.21\pm{0.56}$ & $-0.35\pm{0.21}$ & $-0.59\pm{0.31}$ \\
		&$\sigma, z, N_{gal}$ & $0.70\pm{0.13}$ & $0.37\pm{0.18}$ & $0.13\pm{0.20}$ & $0.01\pm{0.19}$ & $-0.05\pm{0.17}$ & $-0.12\pm{0.67}$ & $-0.44\pm{2.26}$ & $-4.45\pm{7.44}$ \\
		\hline
		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.31}$ & $0.27\pm{0.41}$ & $0.20\pm{0.43}$ & $0.13\pm{0.39}$ & $0.10\pm{0.33}$ & $0.09\pm{0.27}$ & $0.02\pm{0.18}$ & $-0.08\pm{0.09}$ \\
		&$\sigma$ & $0.76\pm{0.28}$ & $0.54\pm{0.29}$ & $0.26\pm{0.31}$ & $0.01\pm{0.31}$ & $-0.13\pm{0.32}$ & $-0.23\pm{0.30}$ & $-0.33\pm{0.29}$ & $-0.32\pm{0.09}$ \\
		&$\sigma, z$ & $0.66\pm{0.13}$ & $0.37\pm{0.23}$ & $0.17\pm{0.26}$ & $0.03\pm{0.25}$ & $-0.09\pm{0.24}$ & $-0.21\pm{0.22}$ & $-0.31\pm{0.25}$ & $-0.28\pm{0.13}$ \\
		&$\sigma, z, N_{gal}$ & $0.57\pm{0.12}$ & $0.28\pm{0.21}$ & $0.09\pm{0.21}$ & $-0.01\pm{0.18}$ & $-0.05\pm{0.16}$ & $-0.08\pm{0.14}$ & $-0.07\pm{0.12}$ & $-0.14\pm{0.13}$ \\
		\hline
		\hline
		\rottext{4}{Prob Based} & Power Law & \nd & \nd & $0.53\pm{0.15}$ & $0.30\pm{0.29}$ & $0.16\pm{0.33}$ & $0.07\pm{0.31}$ & $0.01\pm{0.24}$ & $-0.09\pm{0.13}$ \\
		&$\sigma$ & \nd & \nd & $0.77\pm{0.10}$ & $0.42\pm{0.18}$ & $0.18\pm{0.22}$ & $-0.03\pm{0.22}$ & $-0.18\pm{0.19}$ & $-0.39\pm{0.22}$ \\
		&$\sigma, z$ & \nd & \nd & $0.61\pm{0.12}$ & $0.29\pm{0.19}$ & $0.08\pm{0.22}$ & $-0.11\pm{0.21}$ & $-0.38\pm{1.30}$ & $-0.48\pm{0.27}$ \\
		&$\sigma, z, N_{gal}$ & \nd & \nd & $0.48\pm{0.13}$ & $0.18\pm{0.18}$ & $0.02\pm{0.19}$ & $-0.08\pm{0.19}$ & $-0.50\pm{2.25}$ & $-8.81\pm{7.98}$ \\
		\hline
		\rottext{4}{ML Based} & Power Law & \nd & $0.06\pm{0.80}$ & $0.17\pm{0.39}$ & $0.17\pm{0.41}$ & $0.13\pm{0.38}$ & $0.07\pm{0.32}$ & $0.01\pm{0.24}$ & $-0.09\pm{0.13}$ \\
		&$\sigma$ & \nd & $0.58\pm{0.17}$ & $0.54\pm{0.26}$ & $0.24\pm{0.28}$ & $0.03\pm{0.30}$ & $-0.17\pm{0.30}$ & $-0.26\pm{0.30}$ & $-0.30\pm{0.25}$ \\
		&$\sigma, z$ & \nd & $1.02\pm{0.35}$ & $0.42\pm{0.21}$ & $0.19\pm{0.25}$ & $0.03\pm{0.25}$ & $-0.14\pm{0.25}$ & $-0.25\pm{0.24}$ & $-0.31\pm{0.26}$ \\
		&$\sigma, z, N_{gal}$ & \nd & $0.91\pm{0.45}$ & $0.39\pm{0.19}$ & $0.12\pm{0.21}$ & $-0.00\pm{0.20}$ & $-0.08\pm{0.19}$ & $-0.14\pm{0.19}$ & $-0.21\pm{0.20}$ \\
	\hline
	\end{tabular}
\label{tbl:mass bias}
\end{table*}

We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias}. It should serve as a type of look up table for future cluster observations with HETDEX. The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass. The three horizontal sections represent represent perfect, targeted and survey observations respectively. So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm0.25$ dex.

 A few caveats apply to the numbers given in Table \ref{tbl:mass bias}. While we provide corrections for cluster masses above $10^{15}$, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters. On the oposite end of the cluster mass spectrum, survey observations of low mass clusters are incomplete for two potential reasons. There are very few, if any, clusters detected with survey observations below $10^{12}$. Missing corrections above $10^{12}$ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.

@@

@@

@@

It is the author's hope that this work may be useful to others when conducting their own research. Because this work relies heavily on (often) complex data analysis, and in order to promote transparency and reproducible science, we provide all of the code used to conduct this study at https://github.com/boada/desCluster. Regrettably, large file size prevents including the source data with the analysis routines. The authors are happy to provide them, if requested.
